---
title: "Exploring DHS Datasets"
author: "Nicholas Feng Schaefer"
subtitle: GSE S580
output:
  html_document:
    df_print: paged
---

# Set Up
```{r, message = FALSE}
library(haven)
library(tidyverse)
```


# Background Information

* First two letters ("KE") are the country code.

* Subsequent two letters (e.g. "BR") describe the [data file type](https://dhsprogram.com/data/File-Types-and-Names.cfm#CP_JUMP_10138).

    1. BR: Birth Recode
    
    2. CR: Couples' Recode
    
    3. FW: Field Worker Questionnaire
    
    4. GC: Geospatial Covariates
    
    5. GE: Geographic Data
    
    6. GR: Pregnancy Recode
    
    7. HR: Household Recode
    
    8. IR: Individual (Female) Recode
    
    9. KR: Children's Recode
    
    10. MR: Men's Recode
    
    11. NR: Pregnancy and Postnatal Care Recode
    
    12. PR: Household Member Recode

* The next two characters (e.g. "41") refer to the [phase and number of the survey]("https://dhsprogram.com/data/File-Types-and-Names.cfm#CP_JUMP_10141").

# 2022

## Birth Recode
```{r}
dhs_br_2022 <- read_dta("/Users/nicholas/Desktop/580/KE_2022_DHS_04092024_1933_57803/KEBR8BDT/KEBR8BFL.DTA")
```

## Household Recode
```{r}
dhs_hr_2022 <- read_dta("/Users/nicholas/Desktop/580/KE_2022_DHS_04092024_1933_57803/KEHR8BDT/KEHR8BFL.DTA")
```






