---
title: "sum_stat_avg"
author: "Kim Her"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Dataset

```{r}
suppressMessages(library(readr))
suppressMessages(library(tidyverse))
data_1 <- suppressMessages(read_csv('C:/Users/yengl/OneDrive/Documents/World Bank Project/appended_df.csv'))
data_1 <- data_1 %>% 
    mutate(gender = ifelse(gender == "Male", 1, 0),
           head = ifelse(head == "Yes, I am the head of the household", 1, 0),
           mar = case_when(
               mar == "No, I have never been married" ~ 0,
               mar == "Yes, I am currently married and living together" ~ 1,
               mar == "No, I have never been married" ~ 2
           ),
           educ = case_when(
               educ == "Did not complete primary" ~ 0,
               educ == "Primary" ~ 1,
               educ == "Secondary (Form 4)" ~ 2,
               educ == "Tertiary (university or certificate)" ~ 3
           ),
           insure = case_when(
               insure == "No, I do not have" ~ 0,
               insure == "No insurance" ~ 0,
               insure == "Comprehensive insurance" ~ 1,
               insure == "Third party insurance" ~ 1,
               insure == "Yes, I do have" ~ 1
           ),
           acc = ifelse(acc_med == "No, I have never been in an accident that required medical care", 0, 1))
```

##  Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
age <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean = mean(age, na.rm = TRUE),
    median = median(age, na.rm = TRUE),
    sd = sd(age, na.rm = TRUE),
    min = min(age, na.rm = TRUE),
    max = max(age, na.rm = TRUE)
  )
print(age)

t.test(data_1$age ~ data_1$greenwheel_dummy)
```

##  Gender: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
gender <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean = mean(gender, na.rm = TRUE),
    median = median(gender, na.rm = TRUE),
    sd = sd(gender, na.rm = TRUE),
    min = min(gender, na.rm = TRUE),
    max = max(gender, na.rm = TRUE)
  )
print(gender)

t.test(data_1$gender ~ data_1$greenwheel_dummy)
```

##  Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
educ <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean = mean(educ, na.rm = TRUE),
    median = median(educ, na.rm = TRUE),
    sd = sd(educ, na.rm = TRUE),
    min = min(educ, na.rm = TRUE),
    max = max(educ, na.rm = TRUE)
  )
print(educ)

t.test(data_1$educ ~ data_1$greenwheel_dummy)
```


##  Head of Household: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
head <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean= mean(head, na.rm = TRUE),
    median = median(head, na.rm = TRUE),
    sd = sd(head, na.rm = TRUE),
    min = min(head, na.rm = TRUE),
    max = max(head, na.rm = TRUE)
  )
print(head)

t.test(data_1$head ~ data_1$greenwheel_dummy)
```

##  Marriage: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
mar <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean = mean(mar, na.rm = TRUE),
    median = median(mar, na.rm = TRUE),
    sd = sd(mar, na.rm = TRUE),
    min = min(mar, na.rm = TRUE),
    max = max(mar, na.rm = TRUE)
  )
print(mar)

t.test(data_1$mar ~ data_1$greenwheel_dummy)
```

##  Numbers of Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
dep <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean = mean(dep, na.rm = TRUE),
    median = median(dep, na.rm = TRUE),
    sd= sd(dep, na.rm = TRUE),
    min = min(dep, na.rm = TRUE),
    max = max(dep, na.rm = TRUE)
  )
print(dep)

t.test(data_1$dep ~ data_1$greenwheel_dummy)
```


##  Accident History: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
acc <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean = mean(acc, na.rm = TRUE),
    median = median(acc, na.rm = TRUE),
    sd= sd(acc, na.rm = TRUE),
    min = min(acc, na.rm = TRUE),
    max = max(acc, na.rm = TRUE)
  )
print(acc)

t.test(data_1$acc ~ data_1$greenwheel_dummy)
```


##  Insurance Status: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
insure <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean = mean(insure, na.rm = TRUE),
    median = median(insure, na.rm = TRUE),
    sd= sd(insure, na.rm = TRUE),
    min = min(insure, na.rm = TRUE),
    max = max(insure, na.rm = TRUE)
  )
print(insure)

t.test(data_1$insure ~ data_1$greenwheel_dummy)
```

##  Boda Income: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_boda <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean= mean(daily_income_boda, na.rm = TRUE),
    median = median(daily_income_boda, na.rm = TRUE),
    sd = sd(daily_income_boda, na.rm = TRUE),
    min = min(daily_income_boda, na.rm = TRUE),
    max = max(daily_income_boda, na.rm = TRUE)
  )
print(income_boda)

t.test(data_1$daily_income_boda ~ data_1$greenwheel_dummy)
```

##  Other Income: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_other <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean= mean(other_income, na.rm = TRUE),
    median = median(other_income, na.rm = TRUE),
    sd = sd(other_income, na.rm = TRUE),
    min = min(other_income, na.rm = TRUE),
    max = max(other_income, na.rm = TRUE)
  )
print(income_other)
t.test(data_1$other_income ~ data_1$greenwheel_dummy)
```

##  Gross Income: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_gross <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean= mean(gross_income, na.rm = TRUE),
    median = median(gross_income, na.rm = TRUE),
    sd = sd(gross_income, na.rm = TRUE),
    min = min(gross_income, na.rm = TRUE),
    max = max(gross_income, na.rm = TRUE)
  )
print(income_gross)
t.test(data_1$gross_income ~ data_1$greenwheel_dummy)
```

##  Net Income: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
net <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean= mean(disposable_income, na.rm = TRUE),
    median = median(disposable_income, na.rm = TRUE),
    sd = sd(disposable_income, na.rm = TRUE),
    min = min(disposable_income, na.rm = TRUE),
    max = max(disposable_income, na.rm = TRUE)
  )
print(net)
t.test(data_1$disposable_income ~ data_1$greenwheel_dummy)
```

##  Time Used for Work (Self Reported): Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
work <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean = mean(time_work, na.rm = TRUE),
    median = median(time_work, na.rm = TRUE),
    sd = sd(time_work, na.rm = TRUE),
    min = min(time_work, na.rm = TRUE),
    max = max(time_work, na.rm = TRUE)
  )
print(work)
t.test(data_1$time_work ~ data_1$greenwheel_dummy)
```



##  Time Used for Leisure: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
leisure <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean = mean(leisure, na.rm = TRUE),
    median = median(leisure, na.rm = TRUE),
    sd = sd(leisure, na.rm = TRUE),
    min = min(leisure, na.rm = TRUE),
    max = max(leisure, na.rm = TRUE)
  )

print(leisure)
t.test(data_1$leisure~data_1$greenwheel_dummy)
```

##  Time Used for Home Care: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
home_labor <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean = mean(home_labor, na.rm = TRUE),
    median = median(home_labor, na.rm = TRUE),
    sd = sd(home_labor, na.rm = TRUE),
    min = min(home_labor, na.rm = TRUE),
    max = max(home_labor, na.rm = TRUE)
  )
print(home_labor)
t.test(data_1$home_labor~data_1$greenwheel_dummy)
```

##  Time Used for Sleep: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
sleep <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean= mean(sleep, na.rm = TRUE),
    median = median(sleep, na.rm = TRUE),
    sd = sd(sleep, na.rm = TRUE),
    min = min(sleep, na.rm = TRUE),
    max = max(sleep, na.rm = TRUE)
  )
print(sleep)
t.test(data_1$sleep~data_1$greenwheel_dummy)
```
