---
title: "WB Demo Stat Sum"
author: "Kim Her"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Dataset

```{r}
suppressMessages(library(readr))
suppressMessages(library(tidyverse))
data_1 <- suppressMessages(read_csv('C:/Users/yengl/OneDrive/Documents/World Bank Project/appended_data.csv'))
```

##  Boda Income: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_boda <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_boda_income = mean(daily_income_boda, na.rm = TRUE),
    median_boda_income = median(daily_income_boda, na.rm = TRUE),
    sd_boda_income = sd(daily_income_boda, na.rm = TRUE),
    min_boda_income = min(daily_income_boda, na.rm = TRUE),
    max_boda_income = max(daily_income_boda, na.rm = TRUE)
  )
print(income_boda)

t.test(data_1$daily_income_boda ~ data_1$greenwheel_dummy)
```

##  Other Income: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_other <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_other_income = mean(other_income, na.rm = TRUE),
    median_other_income = median(other_income, na.rm = TRUE),
    sd_other_income = sd(other_income, na.rm = TRUE),
    min_other_income = min(other_income, na.rm = TRUE),
    max_other_income = max(other_income, na.rm = TRUE)
  )
print(income_other)
t.test(data_1$other_income ~ data_1$greenwheel_dummy)
```

##  Gross Income: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_gross <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_gross_income = mean(gross_income, na.rm = TRUE),
    median_gross_income = median(gross_income, na.rm = TRUE),
    sd_gross_income = sd(gross_income, na.rm = TRUE),
    min_gross_income = min(gross_income, na.rm = TRUE),
    max_gross_income = max(gross_income, na.rm = TRUE)
  )
print(income_gross)
t.test(data_1$gross_income ~ data_1$greenwheel_dummy)
```

##  Boda Income Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_boda_age <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_boda_income = mean(daily_income_boda, na.rm = TRUE),
    median_boda_income = median(daily_income_boda, na.rm = TRUE),
    sd_boda_income = sd(daily_income_boda, na.rm = TRUE),
    min_boda_income = min(daily_income_boda, na.rm = TRUE),
    max_boda_income = max(daily_income_boda, na.rm = TRUE)
  )
print(income_boda_age)
```

```{r}
# Find common educ groups
group0 <- unique(data_1$age[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$age[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common age groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$age == i & data_1$greenwheel_dummy == 0 & data_1$daily_income_boda, na.rm = TRUE)
  count_group1 <- sum(data_1$age == i & data_1$greenwheel_dummy == 1 & data_1$daily_income_boda, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$daily_income_boda[data_1$greenwheel_dummy == 0 & data_1$age == i],
      data_1$daily_income_boda[data_1$greenwheel_dummy == 1 & data_1$age == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Age:", i, "\n")
  print(results[[i]])
  cat("\n")
}
```

##  Other Income Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_other_age <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_other_income = mean(other_income, na.rm = TRUE),
    median_other_income = median(other_income, na.rm = TRUE),
    sd_other_income = sd(other_income, na.rm = TRUE),
    min_other_income = min(other_income, na.rm = TRUE),
    max_other_income = max(other_income, na.rm = TRUE)
  )
print(income_other_age)
```

```{r}
# Find common educ groups
group0 <- unique(data_1$age[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$age[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common age groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$age == i & data_1$greenwheel_dummy == 0 & data_1$other_income, na.rm = TRUE)
  count_group1 <- sum(data_1$age == i & data_1$greenwheel_dummy == 1 & data_1$other_income, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$other_income[data_1$greenwheel_dummy == 0 & data_1$age == i],
      data_1$other_income[data_1$greenwheel_dummy == 1 & data_1$age == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Age:", i, "\n")
  print(results[[i]])
  cat("\n")
}
```

##  Gross Income Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_gross_age <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_gross_income = mean(gross_income, na.rm = TRUE),
    median_gross_income = median(gross_income, na.rm = TRUE),
    sd_gross_income = sd(gross_income, na.rm = TRUE),
    min_gross_income = min(gross_income, na.rm = TRUE),
    max_gross_income = max(gross_income, na.rm = TRUE)
  )
print(income_gross_age)

```

```{r}
# Find common educ groups
group0 <- unique(data_1$age[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$age[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common age groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$age == i & data_1$greenwheel_dummy == 0 & data_1$gross_income, na.rm = TRUE)
  count_group1 <- sum(data_1$age == i & data_1$greenwheel_dummy == 1 & data_1$gross_income, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$gross_income[data_1$greenwheel_dummy == 0 & data_1$age == i],
      data_1$gross_income[data_1$greenwheel_dummy == 1 & data_1$age == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Age:", i, "\n")
  print(results[[i]])
  cat("\n")
}
```


##  Boda Income Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_boda_educ <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_boda_income = mean(daily_income_boda, na.rm = TRUE),
    median_boda_income = median(daily_income_boda, na.rm = TRUE),
    sd_boda_income = sd(daily_income_boda, na.rm = TRUE),
    min_boda_income = min(daily_income_boda, na.rm = TRUE),
    max_boda_income = max(daily_income_boda, na.rm = TRUE)
  )
print(income_boda_educ)
```


```{r}
# Find common educ groups
group0 <- unique(data_1$educ[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$educ[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common educ groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 0 & data_1$daily_income_boda, na.rm = TRUE)
  count_group1 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 1 & data_1$daily_income_boda, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$daily_income_boda[data_1$greenwheel_dummy == 0 & data_1$educ == i],
      data_1$daily_income_boda[data_1$greenwheel_dummy == 1 & data_1$educ == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Educ:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Other Income Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_other_educ <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_other_income = mean(other_income, na.rm = TRUE),
    median_other_income = median(other_income, na.rm = TRUE),
    sd_other_income = sd(other_income, na.rm = TRUE),
    min_other_income = min(other_income, na.rm = TRUE),
    max_other_income = max(other_income, na.rm = TRUE)
  )
print(income_other_educ)

```


```{r}
# Find common educ groups
group0 <- unique(data_1$educ[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$educ[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common educ groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 0 & data_1$other_income, na.rm = TRUE)
  count_group1 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 1 & data_1$other_income, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$other_income[data_1$greenwheel_dummy == 0 & data_1$educ == i],
      data_1$other_income[data_1$greenwheel_dummy == 1 & data_1$educ == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Educ:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Gross Income Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_gross_educ <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_gross_income = mean(gross_income, na.rm = TRUE),
    median_gross_income = median(gross_income, na.rm = TRUE),
    sd_gross_income = sd(gross_income, na.rm = TRUE),
    min_gross_income = min(gross_income, na.rm = TRUE),
    max_gross_income = max(gross_income, na.rm = TRUE)
  )
print(income_gross_educ)
```


```{r}
# Find common educ groups
group0 <- unique(data_1$educ[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$educ[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common educ groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 0 & data_1$gross_income, na.rm = TRUE)
  count_group1 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 1 & data_1$gross_income, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$gross_income[data_1$greenwheel_dummy == 0 & data_1$educ == i],
      data_1$gross_income[data_1$greenwheel_dummy == 1 & data_1$educ == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Educ:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Boda Income Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_boda_dep <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_boda_income = mean(daily_income_boda, na.rm = TRUE),
    median_boda_income = median(daily_income_boda, na.rm = TRUE),
    sd_boda_income = sd(daily_income_boda, na.rm = TRUE),
    min_boda_income = min(daily_income_boda, na.rm = TRUE),
    max_boda_income = max(daily_income_boda, na.rm = TRUE)
  )
print(income_boda_dep)

```

```{r}
# Find common dep groups
dep_groups_group0 <- unique(data_1$dep[data_1$greenwheel_dummy == 0])
dep_groups_group1 <- unique(data_1$dep[data_1$greenwheel_dummy == 1])
common_dep_groups <- intersect(dep_groups_group0, dep_groups_group1)

# Loop over common dep groups and perform t-tests
results <- list()
for (dep_value in common_dep_groups) {
  count_group0 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 0, na.rm = TRUE)
  count_group1 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 1, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$daily_income_boda[data_1$greenwheel_dummy == 0 & data_1$dep == dep_value],
      data_1$daily_income_boda[data_1$greenwheel_dummy == 1 & data_1$dep == dep_value]
    )
    results[[as.character(dep_value)]] <- ttest_result
  }
}

# Print the results
for (dep_value in names(results)) {
  cat("Dep:", dep_value, "\n")
  print(results[[dep_value]])
  cat("\n")
}

```

##  Other Income Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_other_dep <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_other_income = mean(other_income, na.rm = TRUE),
    median_other_income = median(other_income, na.rm = TRUE),
    sd_other_income = sd(other_income, na.rm = TRUE),
    min_other_income = min(other_income, na.rm = TRUE),
    max_other_income = max(other_income, na.rm = TRUE)
  )
print(income_other_dep)
```

```{r}
# Find common dep groups
dep_groups_group0 <- unique(data_1$dep[data_1$greenwheel_dummy == 0])
dep_groups_group1 <- unique(data_1$dep[data_1$greenwheel_dummy == 1])
common_dep_groups <- intersect(dep_groups_group0, dep_groups_group1)

# Loop over common dep groups and perform t-tests
results <- list()
for (dep_value in common_dep_groups) {
  count_group0 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 0 & data_1$other_income, na.rm = TRUE)
  count_group1 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 1 & data_1$other_income, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$other_income[data_1$greenwheel_dummy == 0 & data_1$dep == dep_value],
      data_1$other_income[data_1$greenwheel_dummy == 1 & data_1$dep == dep_value]
    )
    results[[as.character(dep_value)]] <- ttest_result
  }
}

# Print the results
for (dep_value in names(results)) {
  cat("Dep:", dep_value, "\n")
  print(results[[dep_value]])
  cat("\n")
}

```

##  Gross Income Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_gross_dep <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_gross_income = mean(gross_income, na.rm = TRUE),
    median_gross_income = median(gross_income, na.rm = TRUE),
    sd_gross_income = sd(gross_income, na.rm = TRUE),
    min_gross_income = min(gross_income, na.rm = TRUE),
    max_gross_income = max(gross_income, na.rm = TRUE)
  )
print(income_gross_dep)
```

```{r}
# Find common dep groups
dep_groups_group0 <- unique(data_1$dep[data_1$greenwheel_dummy == 0])
dep_groups_group1 <- unique(data_1$dep[data_1$greenwheel_dummy == 1])
common_dep_groups <- intersect(dep_groups_group0, dep_groups_group1)

# Loop over common dep groups and perform t-tests
results <- list()
for (dep_value in common_dep_groups) {
  count_group0 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 0 & data_1$gross_income, na.rm = TRUE)
  count_group1 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 1 & data_1$gross_income, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$gross_income[data_1$greenwheel_dummy == 0 & data_1$dep == dep_value],
      data_1$gross_income[data_1$greenwheel_dummy == 1 & data_1$dep == dep_value]
    )
    results[[as.character(dep_value)]] <- ttest_result
  }
}

# Print the results
for (dep_value in names(results)) {
  cat("Dep:", dep_value, "\n")
  print(results[[dep_value]])
  cat("\n")
}

```

##  Time Used for Work: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
work <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_work = mean(time_work, na.rm = TRUE),
    median_work = median(time_work, na.rm = TRUE),
    sd_work = sd(time_work, na.rm = TRUE),
    min_work = min(time_work, na.rm = TRUE),
    max_work = max(time_work, na.rm = TRUE)
  )
print(work)
t.test(data_1$time_work ~ data_1$greenwheel_dummy)
```



##  Time Used for Leisure: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
leisure <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_leisure = mean(leisure, na.rm = TRUE),
    median_leisure = median(leisure, na.rm = TRUE),
    sd_leisure = sd(leisure, na.rm = TRUE),
    min_leisure = min(leisure, na.rm = TRUE),
    max_leisure = max(leisure, na.rm = TRUE)
  )
print(leisure)
t.test(data_1$leisure~data_1$greenwheel_dummy)
```

##  Time Used for Home Care: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
home_labor <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_home = mean(home_labor, na.rm = TRUE),
    median_home = median(home_labor, na.rm = TRUE),
    sd_home = sd(home_labor, na.rm = TRUE),
    min_home = min(home_labor, na.rm = TRUE),
    max_home = max(home_labor, na.rm = TRUE)
  )
print(home_labor)
t.test(data_1$home_labor~data_1$greenwheel_dummy)
```

##  Time Used for Sleep: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
sleep <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_sleep= mean(sleep, na.rm = TRUE),
    median_sleep = median(sleep, na.rm = TRUE),
    sd_sleep = sd(sleep, na.rm = TRUE),
    min_sleep = min(sleep, na.rm = TRUE),
    max_sleep = max(sleep, na.rm = TRUE)
  )
print(sleep)
t.test(data_1$sleep~data_1$greenwheel_dummy)
```

##  Time Used for Work Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
work_age <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_work = mean(time_work, na.rm = TRUE),
    median_work = median(time_work, na.rm = TRUE),
    sd_work = sd(time_work, na.rm = TRUE),
    min_work = min(time_work, na.rm = TRUE),
    max_work = max(time_work, na.rm = TRUE)
  )
print(work_age)
```

```{r}
# Find common educ groups
group0 <- unique(data_1$age[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$age[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common age groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$age == i & data_1$greenwheel_dummy == 0 & data_1$time_work, na.rm = TRUE)
  count_group1 <- sum(data_1$age == i & data_1$greenwheel_dummy == 1 & data_1$time_work, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$time_work[data_1$greenwheel_dummy == 0 & data_1$age == i],
      data_1$time_work[data_1$greenwheel_dummy == 1 & data_1$age == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Age:", i, "\n")
  print(results[[i]])
  cat("\n")
}
```

##  Time Used for Leisure Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
leisure_age <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_leisure = mean(leisure, na.rm = TRUE),
    median_leisure = median(leisure, na.rm = TRUE),
    sd_leisure = sd(leisure, na.rm = TRUE),
    min_leisure = min(leisure, na.rm = TRUE),
    max_leisure = max(leisure, na.rm = TRUE)
  )
print(leisure_age)
```

```{r}
# Find common educ groups
group0 <- unique(data_1$age[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$age[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common age groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$age == i & data_1$greenwheel_dummy == 0 & data_1$leisure, na.rm = TRUE)
  count_group1 <- sum(data_1$age == i & data_1$greenwheel_dummy == 1 & data_1$leisure, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$leisure[data_1$greenwheel_dummy == 0 & data_1$age == i],
      data_1$leisure[data_1$greenwheel_dummy == 1 & data_1$age == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Age:", i, "\n")
  print(results[[i]])
  cat("\n")
}
```

##  Time Used for Home Care Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
home_labor_age <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_home = mean(home_labor, na.rm = TRUE),
    median_home = median(home_labor, na.rm = TRUE),
    sd_home = sd(home_labor, na.rm = TRUE),
    min_home = min(home_labor, na.rm = TRUE),
    max_home = max(home_labor, na.rm = TRUE)
  )
print(home_labor_age)
```

```{r}
# Find common educ groups
group0 <- unique(data_1$age[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$age[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common age groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$age == i & data_1$greenwheel_dummy == 0 & data_1$home_labor, na.rm = TRUE)
  count_group1 <- sum(data_1$age == i & data_1$greenwheel_dummy == 1 & data_1$home_labor, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$home_labor[data_1$greenwheel_dummy == 0 & data_1$age == i],
      data_1$home_labor[data_1$greenwheel_dummy == 1 & data_1$age == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Age:", i, "\n")
  print(results[[i]])
  cat("\n")
}
```

##  Time Used for Sleep Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
sleep_age <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_sleep = mean(sleep, na.rm = TRUE),
    median_sleep = median(sleep, na.rm = TRUE),
    sd_sleep = sd(sleep, na.rm = TRUE),
    min_sleep = min(sleep, na.rm = TRUE),
    max_sleep = max(sleep, na.rm = TRUE)
  )
print(sleep_age)
```

```{r}
# Find common educ groups
group0 <- unique(data_1$educ[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$educ[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common age groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$age == i & data_1$greenwheel_dummy == 0 & data_1$time_work, na.rm = TRUE)
  count_group1 <- sum(data_1$age == i & data_1$greenwheel_dummy == 1 & data_1$time_work, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$time_work[data_1$greenwheel_dummy == 0 & data_1$age == i],
      data_1$time_work[data_1$greenwheel_dummy == 1 & data_1$age == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Age:", i, "\n")
  print(results[[i]])
  cat("\n")
}
```

##  Time Used for Work Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
work_educ <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_work = mean(time_work, na.rm = TRUE),
    median_work = median(time_work, na.rm = TRUE),
    sd_work = sd(time_work, na.rm = TRUE),
    min_work = min(time_work, na.rm = TRUE),
    max_work = max(time_work, na.rm = TRUE)
  )
print(work_educ)
```

```{r}
# Find common educ groups
group0 <- unique(data_1$educ[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$educ[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common educ groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 0 & data_1$time_work, na.rm = TRUE)
  count_group1 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 1 & data_1$time_work, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$time_work[data_1$greenwheel_dummy == 0 & data_1$educ == i],
      data_1$time_work[data_1$greenwheel_dummy == 1 & data_1$educ == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Educ:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Time Used for Leisure Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
leisure_educ <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_leisure = mean(leisure, na.rm = TRUE),
    median_leisure = median(leisure, na.rm = TRUE),
    sd_leisure = sd(leisure, na.rm = TRUE),
    min_leisure = min(leisure, na.rm = TRUE),
    max_leisure = max(leisure, na.rm = TRUE)
  )
print(leisure_educ)
```

```{r}
# Find common educ groups
group0 <- unique(data_1$educ[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$educ[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common educ groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 0 & data_1$leisure, na.rm = TRUE)
  count_group1 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 1 & data_1$leisure, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$leisure[data_1$greenwheel_dummy == 0 & data_1$educ == i],
      data_1$leisure[data_1$greenwheel_dummy == 1 & data_1$educ == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Educ:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Time Used for Home Care Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
home_labor_educ <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_home = mean(home_labor, na.rm = TRUE),
    median_home = median(home_labor, na.rm = TRUE),
    sd_home= sd(home_labor, na.rm = TRUE),
    min_home = min(home_labor, na.rm = TRUE),
    max_home = max(home_labor, na.rm = TRUE)
  )
print(home_labor_educ)
```

```{r}
# Find common educ groups
group0 <- unique(data_1$educ[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$educ[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common educ groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 0 & data_1$home_labor, na.rm = TRUE)
  count_group1 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 1 & data_1$home_labor, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$home_labor[data_1$greenwheel_dummy == 0 & data_1$educ == i],
      data_1$home_labor[data_1$greenwheel_dummy == 1 & data_1$educ == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Educ:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Time Used for Sleep Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
sleep_educ <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_sleep = mean(sleep, na.rm = TRUE),
    median_sleep = median(sleep, na.rm = TRUE),
    sd_sleep = sd(sleep, na.rm = TRUE),
    min_sleep = min(sleep, na.rm = TRUE),
    max_sleep = max(sleep, na.rm = TRUE)
  )
print(sleep_educ)
```

```{r}
# Find common educ groups
group0 <- unique(data_1$educ[data_1$greenwheel_dummy == 0])
group1 <- unique(data_1$educ[data_1$greenwheel_dummy == 1])
common <- intersect(group0, group1)

# Loop over common educ groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 0 & data_1$sleep, na.rm = TRUE)
  count_group1 <- sum(data_1$educ == i & data_1$greenwheel_dummy == 1 & data_1$sleep, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$sleep[data_1$greenwheel_dummy == 0 & data_1$educ == i],
      data_1$sleep[data_1$greenwheel_dummy == 1 & data_1$educ == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Educ:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Time Used for Work Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
work_dep <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_work = mean(time_work, na.rm = TRUE),
    median_work = median(time_work, na.rm = TRUE),
    sd_work = sd(time_work, na.rm = TRUE),
    min_work = min(time_work, na.rm = TRUE),
    max_work = max(time_work, na.rm = TRUE)
  )
print(work_dep)
```

```{r}
# Find common dep groups
dep_groups_group0 <- unique(data_1$dep[data_1$greenwheel_dummy == 0])
dep_groups_group1 <- unique(data_1$dep[data_1$greenwheel_dummy == 1])
common_dep_groups <- intersect(dep_groups_group0, dep_groups_group1)

# Loop over common dep groups and perform t-tests
results <- list()
for (dep_value in common_dep_groups) {
  count_group0 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 0 & data_1$time_work, na.rm = TRUE)
  count_group1 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 1 & data_1$time_work, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$time_work[data_1$greenwheel_dummy == 0 & data_1$dep == dep_value],
      data_1$time_work[data_1$greenwheel_dummy == 1 & data_1$dep == dep_value]
    )
    results[[as.character(dep_value)]] <- ttest_result
  }
}

# Print the results
for (dep_value in names(results)) {
  cat("Dep:", dep_value, "\n")
  print(results[[dep_value]])
  cat("\n")
}

```

##  Time Used for Leisure Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
leisure_dep <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_leisure = mean(leisure, na.rm = TRUE),
    median_leisure = median(leisure, na.rm = TRUE),
    sd_leisure = sd(leisure, na.rm = TRUE),
    min_leisure = min(leisure, na.rm = TRUE),
    max_leisure = max(leisure, na.rm = TRUE)
  )
print(leisure_dep)
```

```{r}
# Find common dep groups
dep_groups_group0 <- unique(data_1$dep[data_1$greenwheel_dummy == 0])
dep_groups_group1 <- unique(data_1$dep[data_1$greenwheel_dummy == 1])
common_dep_groups <- intersect(dep_groups_group0, dep_groups_group1)

# Loop over common dep groups and perform t-tests
results <- list()
for (dep_value in common_dep_groups) {
  count_group0 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 0 & data_1$leisure, na.rm = TRUE)
  count_group1 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 1 & data_1$leisure, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$leisure[data_1$greenwheel_dummy == 0 & data_1$dep == dep_value],
      data_1$leisure[data_1$greenwheel_dummy == 1 & data_1$dep == dep_value]
    )
    results[[as.character(dep_value)]] <- ttest_result
  }
}

# Print the results
for (dep_value in names(results)) {
  cat("Dep:", dep_value, "\n")
  print(results[[dep_value]])
  cat("\n")
}

```

##  Time Used for Home Care Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
home_labor_dep <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_home = mean(home_labor, na.rm = TRUE),
    median_home = median(home_labor, na.rm = TRUE),
    sd_home = sd(home_labor, na.rm = TRUE),
    min_home = min(home_labor, na.rm = TRUE),
    max_home = max(home_labor, na.rm = TRUE)
  )
print(home_labor_dep)
```

```{r}
# Find common dep groups
dep_groups_group0 <- unique(data_1$dep[data_1$greenwheel_dummy == 0])
dep_groups_group1 <- unique(data_1$dep[data_1$greenwheel_dummy == 1])
common_dep_groups <- intersect(dep_groups_group0, dep_groups_group1)

# Loop over common dep groups and perform t-tests
results <- list()
for (dep_value in common_dep_groups) {
  count_group0 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 0 & data_1$home_labor, na.rm = TRUE)
  count_group1 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 1 & data_1$home_labor, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$home_labor[data_1$greenwheel_dummy == 0 & data_1$dep == dep_value],
      data_1$home_labor[data_1$greenwheel_dummy == 1 & data_1$dep == dep_value]
    )
    results[[as.character(dep_value)]] <- ttest_result
  }
}

# Print the results
for (dep_value in names(results)) {
  cat("Dep:", dep_value, "\n")
  print(results[[dep_value]])
  cat("\n")
}

```

##  Time Used for Sleep Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
sleep_dep <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_sleep = mean(sleep, na.rm = TRUE),
    median_sleep = median(sleep, na.rm = TRUE),
    sd_sleep = sd(sleep, na.rm = TRUE),
    min_sleep = min(sleep, na.rm = TRUE),
    max_sleep = max(sleep, na.rm = TRUE)
  )
print(sleep_dep)
```

```{r}
# Find common dep groups
dep_groups_group0 <- unique(data_1$dep[data_1$greenwheel_dummy == 0])
dep_groups_group1 <- unique(data_1$dep[data_1$greenwheel_dummy == 1])
common_dep_groups <- intersect(dep_groups_group0, dep_groups_group1)

# Loop over common dep groups and perform t-tests
results <- list()
for (dep_value in common_dep_groups) {
  count_group0 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 0 & data_1$sleep, na.rm = TRUE)
  count_group1 <- sum(data_1$dep == dep_value & data_1$greenwheel_dummy == 1 & data_1$sleep, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$sleep[data_1$greenwheel_dummy == 0 & data_1$dep == dep_value],
      data_1$sleep[data_1$greenwheel_dummy == 1 & data_1$dep == dep_value]
    )
    results[[as.character(dep_value)]] <- ttest_result
  }
}

# Print the results
for (dep_value in names(results)) {
  cat("Dep:", dep_value, "\n")
  print(results[[dep_value]])
  cat("\n")
}

```

##  Boda Income Based on Hours Worked: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_boda_work <- data_1 %>% group_by(greenwheel_dummy, round(time_work) ) %>%
  summarise(
    mean_boda_income = mean(daily_income_boda, na.rm = TRUE),
    median_boda_income = median(daily_income_boda, na.rm = TRUE),
    sd_boda_income = sd(daily_income_boda, na.rm = TRUE),
    min_boda_income = min(daily_income_boda, na.rm = TRUE),
    max_boda_income = max(daily_income_boda, na.rm = TRUE)
  )
print(income_boda_work)
```

```{r}
# Find common time_work groups
group0 <- unique(round(data_1$time_work[data_1$greenwheel_dummy == 0]))
group1 <- unique(round(data_1$time_work[data_1$greenwheel_dummy == 1]))
common <- intersect(group0, group1)

# Loop over common time_work groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(round(data_1$time_work) == i & data_1$greenwheel_dummy == 0 & data_1$daily_income_boda, na.rm = TRUE)
  count_group1 <- sum(round(data_1$time_work) == i & data_1$greenwheel_dummy == 1 & data_1$daily_income_boda, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$daily_income_boda[data_1$greenwheel_dummy == 0 & round(data_1$time_work) == i],
      data_1$daily_income_boda[data_1$greenwheel_dummy == 1 & round(data_1$time_work) == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Hours Worked:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Other Income Based on Hours Worked: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_other_work <- data_1 %>% group_by(greenwheel_dummy, round(time_work)) %>%
  summarise(
    mean_other_income = mean(other_income, na.rm = TRUE),
    median_other_income = median(other_income, na.rm = TRUE),
    sd_other_income = sd(other_income, na.rm = TRUE),
    min_other_income = min(other_income, na.rm = TRUE),
    max_other_income = max(other_income, na.rm = TRUE)
  )
print(income_other_work)
```

```{r}
# Find common time_work groups
group0 <- unique(round(data_1$time_work[data_1$greenwheel_dummy == 0]))
group1 <- unique(round(data_1$time_work[data_1$greenwheel_dummy == 1]))
common <- intersect(group0, group1)

# Loop over common time_work groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(round(data_1$time_work) == i & data_1$greenwheel_dummy == 0 & data_1$other_income, na.rm = TRUE)
  count_group1 <- sum(round(data_1$time_work) == i & data_1$greenwheel_dummy == 1 & data_1$other_income, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$other_income[data_1$greenwheel_dummy == 0 & round(data_1$time_work) == i],
      data_1$other_income[data_1$greenwheel_dummy == 1 & round(data_1$time_work) == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Hours Worked:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Gross Income Based on Hours Worked: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_gross_work <- data_1 %>% group_by(greenwheel_dummy, round(time_work)) %>%
  summarise(
    mean_gross_income = mean(gross_income, na.rm = TRUE),
    median_gross_income = median(gross_income, na.rm = TRUE),
    sd_gross_income = sd(gross_income, na.rm = TRUE),
    min_gross_income = min(gross_income, na.rm = TRUE),
    max_gross_income = max(gross_income, na.rm = TRUE)
  )
print(income_gross_work)
```

```{r}
# Find common time_work groups
group0 <- unique(round(data_1$time_work[data_1$greenwheel_dummy == 0]))
group1 <- unique(round(data_1$time_work[data_1$greenwheel_dummy == 1]))
common <- intersect(group0, group1)

# Loop over common time_work groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(round(data_1$time_work) == i & data_1$greenwheel_dummy == 0 & data_1$gross_income, na.rm = TRUE)
  count_group1 <- sum(round(data_1$time_work) == i & data_1$greenwheel_dummy == 1 & data_1$gross_income, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$gross_income[data_1$greenwheel_dummy == 0 & round(data_1$time_work) == i],
      data_1$gross_income[data_1$greenwheel_dummy == 1 & round(data_1$time_work) == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Hours Worked:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Boda Income Based on Hours of Leisure: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_boda_leisure <- data_1 %>% group_by(greenwheel_dummy, leisure ) %>%
  summarise(
    mean_boda_income = mean(daily_income_boda, na.rm = TRUE),
    median_boda_income = median(daily_income_boda, na.rm = TRUE),
    sd_boda_income = sd(daily_income_boda, na.rm = TRUE),
    min_boda_income = min(daily_income_boda, na.rm = TRUE),
    max_boda_income = max(daily_income_boda, na.rm = TRUE)
  )
print(income_boda_leisure)
```

```{r}
# Find common leisure groups
group0 <- unique(round(data_1$leisure[data_1$greenwheel_dummy == 0]))
group1 <- unique(round(data_1$leisure[data_1$greenwheel_dummy == 1]))
common <- intersect(group0, group1)

# Loop over common time_work groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(round(data_1$leisure) == i & data_1$greenwheel_dummy == 0 & data_1$daily_income_boda, na.rm = TRUE)
  count_group1 <- sum(round(data_1$leisure) == i & data_1$greenwheel_dummy == 1 & data_1$daily_income_boda, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$daily_income_boda[data_1$greenwheel_dummy == 0 & round(data_1$leisure) == i],
      data_1$daily_income_boda[data_1$greenwheel_dummy == 1 & round(data_1$leisure) == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Hours Leisured:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Other Income Based on Hours of Liesure: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_other_leisure <- data_1 %>% group_by(greenwheel_dummy, leisure) %>%
  summarise(
    mean_other_income = mean(other_income, na.rm = TRUE),
    median_other_income = median(other_income, na.rm = TRUE),
    sd_other_income = sd(other_income, na.rm = TRUE),
    min_other_income = min(other_income, na.rm = TRUE),
    max_other_income = max(other_income, na.rm = TRUE)
  )
print(income_other_leisure)
```

```{r}
# Find common leisure groups
group0 <- unique(round(data_1$leisure[data_1$greenwheel_dummy == 0]))
group1 <- unique(round(data_1$leisure[data_1$greenwheel_dummy == 1]))
common <- intersect(group0, group1)

# Loop over common time_work groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(round(data_1$leisure) == i & data_1$greenwheel_dummy == 0 & data_1$other_income, na.rm = TRUE)
  count_group1 <- sum(round(data_1$leisure) == i & data_1$greenwheel_dummy == 1 & data_1$other_income, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$other_income[data_1$greenwheel_dummy == 0 & round(data_1$leisure) == i],
      data_1$other_income[data_1$greenwheel_dummy == 1 & round(data_1$leisure) == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Hours Leisured:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Gross Income Based on Hours of Leisures: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_gross_leisure <- data_1 %>% group_by(greenwheel_dummy, leisure) %>%
  summarise(
    mean_gross_income = mean(gross_income, na.rm = TRUE),
    median_gross_income = median(gross_income, na.rm = TRUE),
    sd_gross_income = sd(gross_income, na.rm = TRUE),
    min_gross_income = min(gross_income, na.rm = TRUE),
    max_gross_income = max(gross_income, na.rm = TRUE)
  )
print(income_gross_leisure)
```

```{r}
# Find common leisure groups
group0 <- unique(round(data_1$leisure[data_1$greenwheel_dummy == 0]))
group1 <- unique(round(data_1$leisure[data_1$greenwheel_dummy == 1]))
common <- intersect(group0, group1)

# Loop over common time_work groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(round(data_1$leisure) == i & data_1$greenwheel_dummy == 0 & data_1$gross_income, na.rm = TRUE)
  count_group1 <- sum(round(data_1$leisure) == i & data_1$greenwheel_dummy == 1 & data_1$gross_income, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$gross_income[data_1$greenwheel_dummy == 0 & round(data_1$leisure) == i],
      data_1$gross_income[data_1$greenwheel_dummy == 1 & round(data_1$leisure) == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Hours Leisured:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Boda Income Based on Hours of House Work: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_boda_home<- data_1 %>% group_by(greenwheel_dummy, home_labor ) %>%
  summarise(
    mean_boda_income = mean(daily_income_boda, na.rm = TRUE),
    median_boda_income = median(daily_income_boda, na.rm = TRUE),
    sd_boda_income = sd(daily_income_boda, na.rm = TRUE),
    min_boda_income = min(daily_income_boda, na.rm = TRUE),
    max_boda_income = max(daily_income_boda, na.rm = TRUE)
  )
print(income_boda_home)
```

```{r}
# Find common home labor groups
group0 <- unique(round(data_1$home_labor[data_1$greenwheel_dummy == 0]))
group1 <- unique(round(data_1$home_labor[data_1$greenwheel_dummy == 1]))
common <- intersect(group0, group1)

# Loop over common time_work groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(round(data_1$home_labor) == i & data_1$greenwheel_dummy == 0 & data_1$daily_income_boda, na.rm = TRUE)
  count_group1 <- sum(round(data_1$home_labor) == i & data_1$greenwheel_dummy == 1 & data_1$daily_income_boda, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$daily_income_boda[data_1$greenwheel_dummy == 0 & round(data_1$leisure) == i],
      data_1$daily_income_boda[data_1$greenwheel_dummy == 1 & round(data_1$leisure) == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Hours House Work:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Other Income Based on Hours of House Work: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_other_home <- data_1 %>% group_by(greenwheel_dummy, home_labor) %>%
  summarise(
    mean_other_income = mean(other_income, na.rm = TRUE),
    median_other_income = median(other_income, na.rm = TRUE),
    sd_other_income = sd(other_income, na.rm = TRUE),
    min_other_income = min(other_income, na.rm = TRUE),
    max_other_income = max(other_income, na.rm = TRUE)
  )
print(income_other_home)
```

```{r}
# Find common home labor groups
group0 <- unique(round(data_1$home_labor[data_1$greenwheel_dummy == 0]))
group1 <- unique(round(data_1$home_labor[data_1$greenwheel_dummy == 1]))
common <- intersect(group0, group1)

# Loop over common home labor groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(round(data_1$home_labor) == i & data_1$greenwheel_dummy == 0 & !is.na(data_1$other_income))
  count_group1 <- sum(round(data_1$home_labor) == i & data_1$greenwheel_dummy == 1 & !is.na(data_1$other_income))
  
  if (count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$other_income[data_1$greenwheel_dummy == 0 & round(data_1$home_labor) == i],
      data_1$other_income[data_1$greenwheel_dummy == 1 & round(data_1$home_labor) == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Hours House Work:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Gross Income Based on Hours of House Work: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_gross_home <- data_1 %>% group_by(greenwheel_dummy, home_labor) %>%
  summarise(
    mean_gross_income = mean(gross_income, na.rm = TRUE),
    median_gross_income = median(gross_income, na.rm = TRUE),
    sd_gross_income = sd(gross_income, na.rm = TRUE),
    min_gross_income = min(gross_income, na.rm = TRUE),
    max_gross_income = max(gross_income, na.rm = TRUE)
  )
print(income_gross_home)
```

```{r}
# Find common home labor groups
group0 <- unique(round(data_1$home_labor[data_1$greenwheel_dummy == 0]))
group1 <- unique(round(data_1$home_labor[data_1$greenwheel_dummy == 1]))
common <- intersect(group0, group1)

# Loop over common time_work groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(round(data_1$home_labor) == i & data_1$greenwheel_dummy == 0 & data_1$gross_income, na.rm = TRUE)
  count_group1 <- sum(round(data_1$home_labor) == i & data_1$greenwheel_dummy == 1 & data_1$gross_income, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$gross_income[data_1$greenwheel_dummy == 0 & round(data_1$leisure) == i],
      data_1$gross_income[data_1$greenwheel_dummy == 1 & round(data_1$leisure) == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Hours House Work:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Boda Income Based on Hours of Sleep Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_boda_sleep <- data_1 %>% group_by(greenwheel_dummy, sleep ) %>%
  summarise(
    mean_boda_income = mean(daily_income_boda, na.rm = TRUE),
    median_boda_income = median(daily_income_boda, na.rm = TRUE),
    sd_boda_income = sd(daily_income_boda, na.rm = TRUE),
    min_boda_income = min(daily_income_boda, na.rm = TRUE),
    max_boda_income = max(daily_income_boda, na.rm = TRUE)
  )
print(income_boda_sleep)
```

```{r}
# Find common sleep  groups
group0 <- unique(round(data_1$sleep[data_1$greenwheel_dummy == 0]))
group1 <- unique(round(data_1$sleep[data_1$greenwheel_dummy == 1]))
common <- intersect(group0, group1)

# Loop over common time_work groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(round(data_1$sleep) == i & data_1$greenwheel_dummy == 0 & data_1$daily_income_boda, na.rm = TRUE)
  count_group1 <- sum(round(data_1$sleep) == i & data_1$greenwheel_dummy == 1 & data_1$daily_income_boda, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$daily_income_boda[data_1$greenwheel_dummy == 0 & round(data_1$sleep) == i],
      data_1$daily_income_boda[data_1$greenwheel_dummy == 1 & round(data_1$sleep) == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Hours Sleep:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

##  Other Income Based on Hours of Sleep: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_other_sleep <- data_1 %>% group_by(greenwheel_dummy, sleep) %>%
  summarise(
    mean_other_income = mean(other_income, na.rm = TRUE),
    median_other_income = median(other_income, na.rm = TRUE),
    sd_other_income = sd(other_income, na.rm = TRUE),
    min_other_income = min(other_income, na.rm = TRUE),
    max_other_income = max(other_income, na.rm = TRUE)
  )
print(income_other_sleep)
```

```{r}
# Find common leisure groups
group0 <- unique(round(data_1$sleep[data_1$greenwheel_dummy == 0]))
group1 <- unique(round(data_1$sleep[data_1$greenwheel_dummy == 1]))
common <- intersect(group0, group1)

# Loop over common time_work groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(round(data_1$sleep) == i & data_1$greenwheel_dummy == 0 & data_1$other_income, na.rm = TRUE)
  count_group1 <- sum(round(data_1$sleep) == i & data_1$greenwheel_dummy == 1 & data_1$other_income, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$other_income[data_1$greenwheel_dummy == 0 & round(data_1$sleep) == i],
      data_1$other_income[data_1$greenwheel_dummy == 1 & round(data_1$sleep) == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Hours House Work:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```


##  Gross Income Based on Hours of Sleep: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_gross_sleep <- data_1 %>% group_by(greenwheel_dummy, sleep) %>%
  summarise(
    mean_gross_income = mean(gross_income, na.rm = TRUE),
    median_gross_income = median(gross_income, na.rm = TRUE),
    sd_gross_income = sd(gross_income, na.rm = TRUE),
    min_gross_income = min(gross_income, na.rm = TRUE),
    max_gross_income = max(gross_income, na.rm = TRUE)
  )
print(income_gross_sleep)
```

```{r}
# Find common sleep groups
group0 <- unique(round(data_1$sleep[data_1$greenwheel_dummy == 0]))
group1 <- unique(round(data_1$sleep[data_1$greenwheel_dummy == 1]))
common <- intersect(group0, group1)

# Loop over common time_work groups and perform t-tests
results <- list()
for (i in common) {
  count_group0 <- sum(round(data_1$sleep) == i & data_1$greenwheel_dummy == 0 & data_1$gross_income, na.rm = TRUE)
  count_group1 <- sum(round(data_1$sleep) == i & data_1$greenwheel_dummy == 1 & data_1$gross_income, na.rm = TRUE)
  
  if (!is.na(count_group0) && !is.na(count_group1) && count_group0 >= 2 && count_group1 >= 2) {
    ttest_result <- t.test(
      data_1$gross_income[data_1$greenwheel_dummy == 0 & round(data_1$sleep) == i],
      data_1$gross_income[data_1$greenwheel_dummy == 1 & round(data_1$sleep) == i]
    )
    results[[as.character(i)]] <- ttest_result
  }
}

# Print the results
for (i in names(results)) {
  cat("Hours Sleep:", i, "\n")
  print(results[[i]])
  cat("\n")
}

```

