---
title: "WB Demo Stat Sum"
author: "Kim Her"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Dataset

```{r}
library(readr)
library(tidyverse)
data_1 <- read_csv('C:/Users/yengl/OneDrive/Documents/World Bank Project/appended_data.csv')
```

##  Boda Income: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_boda <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_boda_income = mean(daily_income_boda, na.rm = TRUE),
    median_boda_income = median(daily_income_boda, na.rm = TRUE),
    sd_boda_income = sd(daily_income_boda, na.rm = TRUE),
    min_boda_income = min(daily_income_boda, na.rm = TRUE),
    max_boda_income = max(daily_income_boda, na.rm = TRUE)
  )
print(income_boda)
```

##  Other Income: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_other <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_other_income = mean(other_income, na.rm = TRUE),
    median_other_income = median(other_income, na.rm = TRUE),
    sd_other_income = sd(other_income, na.rm = TRUE),
    min_other_income = min(other_income, na.rm = TRUE),
    max_other_income = max(other_income, na.rm = TRUE)
  )
print(income_other)
```

##  Gross Income: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_gross <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_other_income = mean(gross_income, na.rm = TRUE),
    median_other_income = median(gross_income, na.rm = TRUE),
    sd_other_income = sd(gross_income, na.rm = TRUE),
    min_other_income = min(gross_income, na.rm = TRUE),
    max_other_income = max(gross_income, na.rm = TRUE)
  )
print(income_gross)
```

##  Boda Income Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_boda <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_boda_income = mean(daily_income_boda, na.rm = TRUE),
    median_boda_income = median(daily_income_boda, na.rm = TRUE),
    sd_boda_income = sd(daily_income_boda, na.rm = TRUE),
    min_boda_income = min(daily_income_boda, na.rm = TRUE),
    max_boda_income = max(daily_income_boda, na.rm = TRUE)
  )
print(income_boda)
```

##  Other Income Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_other <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_other_income = mean(other_income, na.rm = TRUE),
    median_other_income = median(other_income, na.rm = TRUE),
    sd_other_income = sd(other_income, na.rm = TRUE),
    min_other_income = min(other_income, na.rm = TRUE),
    max_other_income = max(other_income, na.rm = TRUE)
  )
print(income_other)
```

##  Gross Income Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_gross <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_other_income = mean(gross_income, na.rm = TRUE),
    median_other_income = median(gross_income, na.rm = TRUE),
    sd_other_income = sd(gross_income, na.rm = TRUE),
    min_other_income = min(gross_income, na.rm = TRUE),
    max_other_income = max(gross_income, na.rm = TRUE)
  )
print(income_gross)
```

##  Boda Income Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_boda <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_boda_income = mean(daily_income_boda, na.rm = TRUE),
    median_boda_income = median(daily_income_boda, na.rm = TRUE),
    sd_boda_income = sd(daily_income_boda, na.rm = TRUE),
    min_boda_income = min(daily_income_boda, na.rm = TRUE),
    max_boda_income = max(daily_income_boda, na.rm = TRUE)
  )
print(income_boda)
```

##  Other Income Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_other <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_other_income = mean(other_income, na.rm = TRUE),
    median_other_income = median(other_income, na.rm = TRUE),
    sd_other_income = sd(other_income, na.rm = TRUE),
    min_other_income = min(other_income, na.rm = TRUE),
    max_other_income = max(other_income, na.rm = TRUE)
  )
print(income_other)
```

##  Gross Income Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_gross <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_other_income = mean(gross_income, na.rm = TRUE),
    median_other_income = median(gross_income, na.rm = TRUE),
    sd_other_income = sd(gross_income, na.rm = TRUE),
    min_other_income = min(gross_income, na.rm = TRUE),
    max_other_income = max(gross_income, na.rm = TRUE)
  )
print(income_gross)
```

##  Boda Income Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_boda <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_boda_income = mean(daily_income_boda, na.rm = TRUE),
    median_boda_income = median(daily_income_boda, na.rm = TRUE),
    sd_boda_income = sd(daily_income_boda, na.rm = TRUE),
    min_boda_income = min(daily_income_boda, na.rm = TRUE),
    max_boda_income = max(daily_income_boda, na.rm = TRUE)
  )
print(income_boda)
```

##  Other Income Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_other <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_other_income = mean(other_income, na.rm = TRUE),
    median_other_income = median(other_income, na.rm = TRUE),
    sd_other_income = sd(other_income, na.rm = TRUE),
    min_other_income = min(other_income, na.rm = TRUE),
    max_other_income = max(other_income, na.rm = TRUE)
  )
print(income_other)
```

##  Gross Income Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
income_gross <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_other_income = mean(gross_income, na.rm = TRUE),
    median_other_income = median(gross_income, na.rm = TRUE),
    sd_other_income = sd(gross_income, na.rm = TRUE),
    min_other_income = min(gross_income, na.rm = TRUE),
    max_other_income = max(gross_income, na.rm = TRUE)
  )
print(income_gross)
```

##  Time Used for Work: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
work <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_boda_income = mean(time_work, na.rm = TRUE),
    median_boda_income = median(time_work, na.rm = TRUE),
    sd_boda_income = sd(time_work, na.rm = TRUE),
    min_boda_income = min(time_work, na.rm = TRUE),
    max_boda_income = max(time_work, na.rm = TRUE)
  )
print(work)
```

##  Time Used for Leisure: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
leisure <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_other_income = mean(leisure, na.rm = TRUE),
    median_other_income = median(leisure, na.rm = TRUE),
    sd_other_income = sd(leisure, na.rm = TRUE),
    min_other_income = min(leisure, na.rm = TRUE),
    max_other_income = max(leisure, na.rm = TRUE)
  )
print(leisure)
```

##  Time Used for Home Care: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
home_labor <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_other_income = mean(home_labor, na.rm = TRUE),
    median_other_income = median(home_labor, na.rm = TRUE),
    sd_other_income = sd(home_labor, na.rm = TRUE),
    min_other_income = min(home_labor, na.rm = TRUE),
    max_other_income = max(home_labor, na.rm = TRUE)
  )
print(home_labor)
```

##  Time Used for Sleep: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
sleep <- data_1 %>% group_by(greenwheel_dummy) %>%
  summarise(
    mean_other_income = mean(sleep, na.rm = TRUE),
    median_other_income = median(sleep, na.rm = TRUE),
    sd_other_income = sd(sleep, na.rm = TRUE),
    min_other_income = min(sleep, na.rm = TRUE),
    max_other_income = max(sleep, na.rm = TRUE)
  )
print(sleep)
```

##  Time Used for Work Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
work <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_boda_income = mean(time_work, na.rm = TRUE),
    median_boda_income = median(time_work, na.rm = TRUE),
    sd_boda_income = sd(time_work, na.rm = TRUE),
    min_boda_income = min(time_work, na.rm = TRUE),
    max_boda_income = max(time_work, na.rm = TRUE)
  )
print(work)
```

##  Time Used for Leisure Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
leisure <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_other_income = mean(leisure, na.rm = TRUE),
    median_other_income = median(leisure, na.rm = TRUE),
    sd_other_income = sd(leisure, na.rm = TRUE),
    min_other_income = min(leisure, na.rm = TRUE),
    max_other_income = max(leisure, na.rm = TRUE)
  )
print(leisure)
```

##  Time Used for Home Care Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
home_labor <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_other_income = mean(home_labor, na.rm = TRUE),
    median_other_income = median(home_labor, na.rm = TRUE),
    sd_other_income = sd(home_labor, na.rm = TRUE),
    min_other_income = min(home_labor, na.rm = TRUE),
    max_other_income = max(home_labor, na.rm = TRUE)
  )
print(home_labor)
```

##  Time Used for Sleep Based on Age: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
sleep <- data_1 %>% group_by(greenwheel_dummy, age) %>%
  summarise(
    mean_other_income = mean(sleep, na.rm = TRUE),
    median_other_income = median(sleep, na.rm = TRUE),
    sd_other_income = sd(sleep, na.rm = TRUE),
    min_other_income = min(sleep, na.rm = TRUE),
    max_other_income = max(sleep, na.rm = TRUE)
  )
print(sleep)
```

##  Time Used for Work Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
work <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_boda_income = mean(time_work, na.rm = TRUE),
    median_boda_income = median(time_work, na.rm = TRUE),
    sd_boda_income = sd(time_work, na.rm = TRUE),
    min_boda_income = min(time_work, na.rm = TRUE),
    max_boda_income = max(time_work, na.rm = TRUE)
  )
print(work)
```

##  Time Used for Leisure Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
leisure <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_other_income = mean(leisure, na.rm = TRUE),
    median_other_income = median(leisure, na.rm = TRUE),
    sd_other_income = sd(leisure, na.rm = TRUE),
    min_other_income = min(leisure, na.rm = TRUE),
    max_other_income = max(leisure, na.rm = TRUE)
  )
print(leisure)
```

##  Time Used for Home Care Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
home_labor <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_other_income = mean(home_labor, na.rm = TRUE),
    median_other_income = median(home_labor, na.rm = TRUE),
    sd_other_income = sd(home_labor, na.rm = TRUE),
    min_other_income = min(home_labor, na.rm = TRUE),
    max_other_income = max(home_labor, na.rm = TRUE)
  )
print(home_labor)
```

##  Time Used for Sleep Based on Education: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
sleep <- data_1 %>% group_by(greenwheel_dummy, educ) %>%
  summarise(
    mean_other_income = mean(sleep, na.rm = TRUE),
    median_other_income = median(sleep, na.rm = TRUE),
    sd_other_income = sd(sleep, na.rm = TRUE),
    min_other_income = min(sleep, na.rm = TRUE),
    max_other_income = max(sleep, na.rm = TRUE)
  )
print(sleep)
```

##  Time Used for Work Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
work <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_boda_income = mean(time_work, na.rm = TRUE),
    median_boda_income = median(time_work, na.rm = TRUE),
    sd_boda_income = sd(time_work, na.rm = TRUE),
    min_boda_income = min(time_work, na.rm = TRUE),
    max_boda_income = max(time_work, na.rm = TRUE)
  )
print(work)
```

##  Time Used for Leisure Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
leisure <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_other_income = mean(leisure, na.rm = TRUE),
    median_other_income = median(leisure, na.rm = TRUE),
    sd_other_income = sd(leisure, na.rm = TRUE),
    min_other_income = min(leisure, na.rm = TRUE),
    max_other_income = max(leisure, na.rm = TRUE)
  )
print(leisure)
```

##  Time Used for Home Care Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
home_labor <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_other_income = mean(home_labor, na.rm = TRUE),
    median_other_income = median(home_labor, na.rm = TRUE),
    sd_other_income = sd(home_labor, na.rm = TRUE),
    min_other_income = min(home_labor, na.rm = TRUE),
    max_other_income = max(home_labor, na.rm = TRUE)
  )
print(home_labor)
```

##  Time Used for Sleep Based on Dependents: Greenwheel vs Just Riders
JR:0
GW: 1

```{r}
sleep <- data_1 %>% group_by(greenwheel_dummy, dep) %>%
  summarise(
    mean_other_income = mean(sleep, na.rm = TRUE),
    median_other_income = median(sleep, na.rm = TRUE),
    sd_other_income = sd(sleep, na.rm = TRUE),
    min_other_income = min(sleep, na.rm = TRUE),
    max_other_income = max(sleep, na.rm = TRUE)
  )
print(sleep)
```

