---
title: "Matching Model"
author: "Nicholas Feng Schaefer"
date: "`r Sys.Date()`"
output: html_document
---

# Set Up
```{r, message=FALSE}
library(tidyverse)
library(Matching)
library(readxl)
```

# Loading Dataset
```{r, message=FALSE}
df <- read_xlsx('/Users/nicholas/Desktop/Cal_Poly_SLO/5-World_Bank/Data/merged_data/appended_df.xlsx')
```

```{r}
df <- df %>% 
    filter(disposable_income <= mean(df$disposable_income, na.rm = TRUE) + 3*sd(df$disposable_income, na.rm = TRUE))
```

# Quick Summary Statistics
```{r}
df %>% 
    group_by(greenwheel_dummy) %>% 
    summarize(mean_disposable_income = mean(disposable_income))
```

```{r}
df %>% 
    group_by(greenwheel_dummy) %>% 
    summarize(mean_age = mean(age, na.rm = TRUE))
```

```{r}
df %>% 
    group_by(greenwheel_dummy) %>% 
    summarize(mean_educ = mean(educ, na.rm = TRUE))
```

# Matching

## Matching on Age and Education
```{r}
df1 <- df[!is.na(df$disposable_income) &
         !is.na(df$age) &
         !is.na(df$educ), ]
```

```{r}
matching_mod1 <- Match(Y = df1$disposable_income,
                       Tr = df1$greenwheel_dummy,
                       X = df1[,c("age", "educ")],
                       M = 1,
                       estimand = "ATE")

summary(matching_mod1)
```

## Keep Adding Covariates

### `insure`
```{r}
df2 <- df[complete.cases(df[, c("disposable_income", "age", "educ", "insure")]), ]
```

```{r}
matching_mod2 <- Match(Y = df2$disposable_income,
                       Tr = df2$greenwheel_dummy,
                       X = df2[,c("age", "educ", "insure")],
                       M = 1,
                       estimand = "ATE")

summary(matching_mod2)
```

### `dep`
```{r}
df3 <- df[complete.cases(df[, c("disposable_income", "age", "educ", "insure", "dep")]), ]
```

```{r}
covariates <- df3 %>% 
    dplyr::select(age, educ, insure, dep)

matching_mod3 <- Match(Y = df3$disposable_income,
                       Tr = df3$greenwheel_dummy,
                       X = covariates,
                       M = 1,
                       estimand = "ATE")

summary(matching_mod3)
```

```{r}
df_subset <- df[complete.cases(df[, c("disposable_income", "age", "educ", "dep")]), ]

covariates <- df_subset %>% 
    dplyr::select(age, educ, dep)

matching_mod <- Match(Y = df_subset$disposable_income,
                       Tr = df_subset$greenwheel_dummy,
                       X = covariates,
                       M = 1,
                       estimand = "ATE")

summary(matching_mod)
```

Adding `dep` turns the ATE positive.

```{r}
df %>% 
    group_by(greenwheel_dummy) %>% 
    summarize(mean_dependents = mean(dep, na.rm = TRUE))
```

### `leisure`
```{r}
df_subset <- df[complete.cases(df[, c("disposable_income", "age", "educ", "leisure")]), ]

covariates <- df_subset %>% 
    dplyr::select(age, educ, leisure)

matching_mod <- Match(Y = df_subset$disposable_income,
                       Tr = df_subset$greenwheel_dummy,
                       X = covariates,
                       M = 1,
                       estimand = "ATE")

summary(matching_mod)
```

This says that individuals in the GreenWheel program, with similar levels of leisure time, have a positive ATE. This might indicate that GreenWheel riders earn more per hour but less overall since individuals in the JustRider group work longer hours.

```{r}
df %>% 
    group_by(greenwheel_dummy) %>% 
    summarize(mean_time_worked = mean(time_work, na.rm = TRUE))
```

Let's try matching on the time worked.
```{r}
df_subset <- df[complete.cases(df[, c("disposable_income", "age", "educ", "time_work")]), ]

covariates <- df_subset %>% 
    dplyr::select(age, educ, time_work)

matching_mod <- Match(Y = df_subset$disposable_income,
                       Tr = df_subset$greenwheel_dummy,
                       X = covariates,
                       M = 1,
                       estimand = "ATE")

summary(matching_mod)
```

```{r}
df %>% 
    mutate(total_time = time_work + leisure + sleep + home_labor) %>% 
    ggplot(aes(x = total_time)) + 
    geom_histogram(bins = 24) +
    scale_x_continuous(limits = c(0, 24))
```

### `acc_med`
```{r}
df_subset <- df[complete.cases(df[, c("disposable_income", "age", "educ", "acc_med")]), ]

covariates <- df_subset %>% 
    dplyr::select(age, educ, acc_med)

matching_mod <- Match(Y = df_subset$disposable_income,
                       Tr = df_subset$greenwheel_dummy,
                       X = covariates,
                       M = 1,
                       estimand = "ATE")

summary(matching_mod)
```

## Matching Using More Covariates
```{r}
df2 <- df[!is.na(df$disposable_income) &
         !is.na(df$greenwheel_dummy) &
         !is.na(df$age) &
         !is.na(df$dep) &
         !is.na(df$leisure) &
         !is.na(df$educ) &
         !is.na(df$acc_med) &
         !is.na(df$insure), ]
```

```{r}
covariates <- df2 %>% 
    dplyr::select(age, educ, insure, acc_med, dep, leisure)

matching_mod2 <- Match(Y = df2$disposable_income,
                       Tr = df2$greenwheel_dummy,
                       X = covariates,
                       M = 1,
                       estimand = "ATE")

summary(matching_mod2)
```

## Matching On P-Scores
```{r}
df_pscore <- df[complete.cases(df[, c("age", "educ", "insure", "acc_med", "dep", "leisure")]), ]
```

```{r}
logit_mod1 <- glm(greenwheel_dummy ~ age + educ + insure + acc_med + dep + leisure, data = df_pscore, family = binomial(link = "logit"))
summary(logit_mod1)
```

```{r}
p_score <- predict(logit_mod1, newdata = df_pscore, type = "response")

df_pscore <- cbind(df_pscore, p_score)
```

```{r}
df_pscore <- df_pscore[!is.na(df_pscore$disposable_income),]

matching_mod3 <- Match(Y = df_pscore$disposable_income,
                       Tr = df_pscore$greenwheel_dummy,
                       X = df_pscore$p_score,
                       M = 1,
                       estimand = "ATE")

summary(matching_mod3)
```

